Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-02 appendix.tex
Solving problem in appendix

Replicability: Follow instructions at the following link: \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/wiki/How-to-reproduce-experiments-on-TITAN} to prepare the environment on Titan.
Launch:
\begin{itemize}
\item python dispatcher.py 250 250 120 etc/input_100 to replicate experiments with 250 nodes;
\item python dispatcher.py 500 500 120 etc/input_100 to replicate experiments with 500 nodes;
\item python dispatcher.py 1000 1000 120 etc/input_100 to replicate experiments with 1000 nodes;
\item python dispatcher.py 2000 2000 120 etc/input_100 to replicate experiments with 2000 nodes.
\end{itemize}

@@

Replicability: Follow instructions at the following link: \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/wiki/How-to-reproduce-experiments-on-TITAN} to prepare the environment on Titan.
Launch:
\begin{itemize}
\item python dispatcher.py 256 1280 256 180 etc/input_16 to replicate experiments with 256 nodes;
\item python dispatcher.py 512 2560 512 180 etc/input_16 to replicate experiments with 512 nodes;
\item python dispatcher.py 1024 5120 180 etc/input_16 to replicate experiments with 1024 nodes;
\item python dispatcher.py 2048 10240 180 etc/input_16 to replicate experiments with 2048 nodes.
\end{itemize}

@@

Replicability: Follow instructions at the following link: \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/wiki/How-to-reproduce-experiments-on-TITAN} to prepare the environment on Titan.
Launch:
\begin{itemize}
\item python dispatcher.py 256  2048 256 180 etc/input_16 to replicate experiments with 256 nodes;
\item python dispatcher.py 512 2048 512 180 etc/input_16 to replicate experiments with 512 nodes;
\item python dispatcher.py 1024 2048 180 etc/input_16 to replicate experiments with 1024 nodes;
\item python dispatcher.py 2048 2048 180 etc/input_16 to replicate experiments with 2048 nodes.
\end{itemize}

>>>>

Replicability: Follow instructions at the following link: \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/wiki/How-to-reproduce-experiments-on-TITAN} to prepare the environment on Titan.
Launch:
\begin{itemize}
\item python dispatcher.py 250 250 120 etc/input\_100 to replicate experiments with 250 nodes;
\item python dispatcher.py 500 500 120 etc/input\_100 to replicate experiments with 500 nodes;
\item python dispatcher.py 1000 1000 120 etc/input\_100 to replicate experiments with 1000 nodes;
\item python dispatcher.py 2000 2000 120 etc/input\_100 to replicate experiments with 2000 nodes.
\end{itemize}

@@

Replicability: Follow instructions at the following link: \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/wiki/How-to-reproduce-experiments-on-TITAN} to prepare the environment on Titan.
Launch:
\begin{itemize}
\item python dispatcher.py 256 1280 256 180 etc/input\_16 to replicate experiments with 256 nodes;
\item python dispatcher.py 512 2560 512 180 etc/input\_16 to replicate experiments with 512 nodes;
\item python dispatcher.py 1024 5120 180 etc/input\_16 to replicate experiments with 1024 nodes;
\item python dispatcher.py 2048 10240 180 etc/input\_16 to replicate experiments with 2048 nodes.
\end{itemize}

@@

Replicability: Follow instructions at the following link: \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/wiki/How-to-reproduce-experiments-on-TITAN} to prepare the environment on Titan.
Launch:
\begin{itemize}
\item python dispatcher.py 256  2048 256 180 etc/input\_16 to replicate experiments with 256 nodes;
\item python dispatcher.py 512 2048 512 180 etc/input\_16 to replicate experiments with 512 nodes;
\item python dispatcher.py 1024 2048 180 etc/input\_16 to replicate experiments with 1024 nodes;
\item python dispatcher.py 2048 2048 180 etc/input\_16 to replicate experiments with 2048 nodes.
\end{itemize}
